\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}

%opening
\title{CSCI 491/591, Group Project Part 0}
\author{Tao Huang and James Soddy}

\begin{document}

\maketitle

Our group intend to work together to complete all portions of the project.
We have some amount of flexibility in our plans, and we are
still open to the possibility of merging with another group or taking on
another member.

\section{P1 and P2}

During the exploration phase, Tao and James will work together to select
several options for our project. Tao's statistics background and knowledge
of data will help us to find data sets which will make for an interesting
project. James will also help with finding and discussing data sets. Both
group members will help assemble ideas and information, but James will have
primary responsibility for completing the write-up. 

\section{P3}

James and Tao will work together to select the visualization which
will best represent our data. Both will be responsible for processing
the data, but Tao will have primary responsibility for generating the
visualizations.

\section{P4}

For our group's presentation, Tao and James will both participate in
planning and presenting the data. Tao's focus will likely be more on numbers
and graphs while James will focus more on the explanation.

\section{P5 - P7}

Through the final sections, we will frequently discuss our data and
keep notes on  what we have done and what we need. Tao will have primary
responsibility for providing interpretation of our data analysis results,
while James will be accumulating our work and putting it into a form that
will be suitable for turning in. Tao will take the lead in our group
presentation in class, while James will have final responsibility for
completing our written deliverable.

\section{Conclusion}

We feel that our very different skill sets will work well together so
that we can complete an interesting project. We are looking forward to
collaborating again.

\end{document}

